---
output:
  BiocStyle::html_document
---

<!--
%\VignetteIndexEntry{Bioconductor style for HTML documents}
%\VignettePackage{BiocStyle}
%\VignetteEngine{knitr::knitr}
-->

# Bioconductor style for HTML documents

```{r style, echo = FALSE}
BiocStyle::markdown()
```

## Use

To enable Bioconductor style in your Markdown vignettes, you need to

- add the following to the `DESCRIPTION` file

        VignetteBuilder: knitr
        Suggests: BiocStyle, knitr
    
- specify the vignette engine `\VignetteEngine{knitr::knitr}` in the `Rmd` files (inside HTML comments)
- add the following code chunk at the beginning of your `Rmd` vignettes

        ```{r, echo = FALSE , results = 'asis'}
        cat("```{r style, echo = FALSE}\nBiocStyle::markdown()\n```")
        ```
        
### Adding custom style sheets

Additional style sheets can be used by providing them to the `BiocStyle::markdown` function. For example, to include the `my.css` file use

    ```{r, echo = FALSE , results = 'asis'}
    cat("```{r style, echo = FALSE}\nBiocStyle::markdown(css.files = c('my.css'))\n```")
    ```

## Use with R Markdown v2

If you are using RStudio to "knit" the document or compile it through the `rmarkdown` package you need to include, in addition to the code chunk calling `BiocStyle::markdown()`, the metadata header defining the output format. Add at the very top of your document

    ---
    output:
      BiocStyle::html_document
    ---

The `BiocStyle::html_document` output format extends the `rmarkdown` build-in `html_document` format and you can use any of its parameters, e.g. to add the table of contents and a custom CSS file use

    ---
    output:
      BiocStyle::html_document:
        toc: true
        css: my.css
    ---

## Using Math Symbols

You can write math expressions the same way you would in `Latex`, except some differences in escaping them.

### Inline
For inline formulas use `$P(x) = \frac{1}{2}$` or `\(P(x) = \frac{1}{2}\)`, which both render as $P(x) = \frac{1}{2}$.

### Standalone

Math can be displayed in a separate line by writing `$$P(x) = \frac{1}{2}$$` or `\[P(x) = \frac{1}{2}.\]`, which both result in $$P(x) = \frac{1}{2}.$$

## BioC macros

```{r macro, echo = FALSE}
macro = function(txt) sprintf("`` `r %s` ``", txt)
```

BiocStyle introduces the following macros useful when refering to R packages:

* `r macro("Biocpkg('IRanges')")` for Bioconductor software packages, including a link to the release version landing page, `r Biocpkg("IRanges")`

* `r macro("Biocannopkg('org.Hs.eg.db')")` for Bioconductor annotation packages, including a link to the release version landing page, `r Biocannopkg("org.Hs.eg.db")`
  
* `r macro("Biocexptpkg('parathyroidSE')")` for Bioconductor experiment data packages, including a link to the release version landing page, `r Biocexptpkg('parathyroidSE')`

* `r macro("CRANpkg('data.table')")` for R packages available on CRAN, including a link to the FHCRC CRAN mirror landing page, `r CRANpkg('data.table')`
