<!--
%\VignetteIndexEntry{Bioconductor style for HTML documents}
%\VignettePackage{BiocStyle}
%\VignetteEngine{knitr::knitr}
-->

```{r style, echo = FALSE}
BiocStyle::markdown()
```

# Bioconductor style for HTML documents

To enable Bioconductor style in your Markdown vignettes, you need to

- add the following to the `DESCRIPTION` file

        VignetteBuilder: knitr
        Suggests: BiocStyle, knitr
    
- specify the vignette engine `\VignetteEngine{knitr::knitr}` in the `Rmd` files (inside HTML comments)
- add the following code chunk to your `Rmd` vignettes

        ```{r, echo = FALSE , results = 'asis'}
        cat("```{r style, echo = FALSE}\nBiocStyle::markdown()\n```")
        ```
        
The exact location of the above code chunk doesn't really matter, however, to maintain a clear presentation it is good practive to have it as the first code chunk.

## Extending the default style

Additional custom style sheets can be used by providing them to the `BiocStyle::markdown` function. For example, to include the `my.css` file use

    ```{r, echo = FALSE , results = 'asis'}
    cat("```{r style, echo = FALSE}\nBiocStyle::markdown(css.files = c('my.css'))\n```")
    ```

## Using Math Symbols

You can write math expressions the same way you would in `Latex`, except some differences in escaping them.

### Inline
For inline formulas use `$P(x) = \frac{1}{2}$` or `\(P(x) = \frac{1}{2}\)`, which both render as $P(x) = \frac{1}{2}$.

### Standalone

Math can be displayed in a separate line by writing `$$P(x) = \frac{1}{2}$$` or `\[P(x) = \frac{1}{2}.\]`, which both result in $$P(x) = \frac{1}{2}.$$
